Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-12 xrb2/paper.tex
add note
Added 1000Hz and 250Hz info to Table 1 for completeness

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:500Hz_runs} Temperature properties of the 500~Hz simulations.}
	\tablehead{\colhead{run} & \colhead{$\delta T$ (K)} & \colhead{$T_\mathrm{hi}$ (K)} & \colhead{$T_\mathrm{star}$ (K)}} 
	\startdata
	{\tt flame\_wave\_500}      & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	% Do we want the 100 Hz run in here as well, for completeness (and so we have a name to reference)?
	{\tt flame\_wave\_500\_2E8} & $1.2\times 10^9$ & $2\times 10^8$ & $2\times 10^8$ \\
	{\tt flame\_wave\_500\_3E8} & $1.1\times 10^9$ & $3\times 10^8$ & $3\times 10^8$ \\
	{\tt flame\_wave\_500\_4E8} & $10^9$ & $4\times 10^8$ & $4\times 10^8$ \\
	\enddata
	%
\end{deluxetable}

>>>>

In our latest set of runs, we explore a variety of initial rotation rate and temperature conditions for the flame. The initial conditions are given in Table \ref{table:500Hz_runs}.

@@

\begin{deluxetable}{lrrrrr}
	\tablecaption{\label{table:500Hz_runs} Rotation rate and temperature properties of the simulations.}
	\tablehead{\colhead{run} & \colhead{Rotation Rate (Hz)} & \colhead{$\delta T$ (K)} & \colhead{$T_\mathrm{hi}$ (K)} & \colhead{$T_\mathrm{star}$ (K)}} 
	\startdata
	{\tt flame\_wave\_1000}     & $1000$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	{\tt flame\_wave\_500}      & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	{\tt flame\_wave\_500\_2E8} & $500$ & $1.2\times 10^9$ & $2\times 10^8$ & $2\times 10^8$ \\
	{\tt flame\_wave\_500\_3E8} & $500$ & $1.1\times 10^9$ & $3\times 10^8$ & $3\times 10^8$ \\
	{\tt flame\_wave\_500\_4E8} & $500$ & $10^9$ & $4\times 10^8$ & $4\times 10^8$ \\
	{\tt flame\_wave\_250}      & $250$ & $1.2\times 10^9$ & $2\times 10^8$ & $10^8$ \\
	\enddata
\end{deluxetable}
